Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2022-01-14 Supplemental-Material-B-Annotated-Analysis.Rmd
notes added

as.numeric(workerInteractionType$NonOutgroupInteraction)

ggplot(workerAttInteractionType, aes(y=Attitude, x=OutgroupInteraction, group = interaction(OutgroupInteraction, NonOutgroupInteraction), fill=NonOutgroupInteraction))+
  geom_violin(trim = T, width=.8, position = position_dodge(0.8)) +
  geom_boxplot(width=0.04,
               position = position_dodge(.8),
               outlier.colour = NULL, 
               outlier.shape = NA, 
               notch=F, fill="black", 
               lwd=1, color="black") + 
  # geom_jitter(width = 0.15,
  #            shape=18,
  #            alpha=.2, size=1) +
  stat_summary(fun.y=mean, 
               geom="point", 
               shape=16, 
               size=1, 
               position = position_dodge(0.8),
               colour="white") +
  #stat_summary(fun.data="mean_sdl",  
  #             fun.args = list(mult=1), 
  #             geom="pointrange", 
  #             color = "red", 
  #             width=.2)+
  stat_summary(geom = "crossbar", 
               width=0.04, 
               fatten=0, 
               position = position_dodge(0.8),
               color="white", 
               fun.data = function(x){ return(c(y=median(x), 
                                                ymin=median(x), 
                                                ymax=median(x))) })+
  ylab("Outgroup Attitudes")+
  xlab("Outgroup Interaction") +
  ggtitle("Violin Plot:\nOutgroup Attitudes by Interaction Type")+
  scale_y_continuous(
    limits = c(0, 100),
    breaks = c(0, 15, 30, 40, 50, 60, 70, 85, 100),
    labels = c(
      "Very cold or unfavorable feelings 0°",
      "Quite cold and unfavorable feelings 15°",
      "Fairly cold and unfavorable feelings 30°",
      "A bit cold and unfavorable feelings 40°",
      "No feeling at all 50°",
      "A bit warm and favorable feelings 60°",
      "Fairly warm and favorable feelings 70° ",
      "Quite warm and favorable feelings 85° ",
      "Very warm and favorable feelings 100° "
    )
  ) +
  #coord_flip()+
  scale_fill_brewer(palette = "Pastel2", name = "Non-Outgroup Interaction")+
  theme_Publication()+
  theme(strip.background =element_rect(fill="black", color="black"),
        strip.text = element_text(colour = 'white', face="bold"))#,
        #panel.border = element_rect(color="grey"),
        #legend.position="none")

workerContactType <- dtWorker$full %>%
  group_by(
    Contact_dum,
    inNonDutch
  ) %>%
  summarise(
    n = n(),
    AttitudeM = mean(thermometerDutch_1, na.rm = T),
    AttitudeSD = sd(thermometerDutch_1, na.rm = T),
    AttitudeSE = AttitudeSD / sqrt(n),
    AttitudeLwr = AttitudeM - 1.96 * AttitudeSE,
    AttitudeUpr = AttitudeM + 1.96 * AttitudeSE
  ) %>%
  ungroup() %>%
  mutate(InteractionType = paste(
    ifelse(Contact_dum == 1, "Out", "NoOut"),
    ifelse(inNonDutch == 1, "In", "NoIn"),
    sep = ", "
  ))

>>>>

# violin plot of attitudes by interaction type group
ggplot(workerAttInteractionType, aes(y=Attitude, x=OutgroupInteraction, group = interaction(OutgroupInteraction, NonOutgroupInteraction), fill=NonOutgroupInteraction))+
  geom_violin(trim = T, width=.8, position = position_dodge(0.8)) +
  geom_boxplot(width=0.04,
               position = position_dodge(.8),
               outlier.colour = NULL, 
               outlier.shape = NA, 
               notch=F, fill="black", 
               lwd=1, color="black") + 
  # geom_jitter(width = 0.15,
  #            shape=18,
  #            alpha=.2, size=1) +
  stat_summary(fun.y=mean, 
               geom="point", 
               shape=16, 
               size=1, 
               position = position_dodge(0.8),
               colour="white") +
  #stat_summary(fun.data="mean_sdl",  
  #             fun.args = list(mult=1), 
  #             geom="pointrange", 
  #             color = "red", 
  #             width=.2)+
  stat_summary(geom = "crossbar", 
               width=0.04, 
               fatten=0, 
               position = position_dodge(0.8),
               color="white", 
               fun.data = function(x){ return(c(y=median(x), 
                                                ymin=median(x), 
                                                ymax=median(x))) })+
  ylab("Outgroup Attitudes")+
  xlab("Outgroup Interaction") +
  ggtitle("Violin Plot:\nOutgroup Attitudes by Interaction Type")+
  scale_y_continuous(
    limits = c(0, 100),
    breaks = c(0, 15, 30, 40, 50, 60, 70, 85, 100),
    labels = c(
      "Very cold or unfavorable feelings 0°",
      "Quite cold and unfavorable feelings 15°",
      "Fairly cold and unfavorable feelings 30°",
      "A bit cold and unfavorable feelings 40°",
      "No feeling at all 50°",
      "A bit warm and favorable feelings 60°",
      "Fairly warm and favorable feelings 70° ",
      "Quite warm and favorable feelings 85° ",
      "Very warm and favorable feelings 100° "
    )
  ) +
  #coord_flip()+
  scale_fill_brewer(palette = "Pastel2", name = "Non-Outgroup Interaction")+
  theme_Publication()+
  theme(strip.background =element_rect(fill="black", color="black"),
        strip.text = element_text(colour = 'white', face="bold"))#,
        #panel.border = element_rect(color="grey"),
        #legend.position="none")

# summarize by interaction type group
workerContactType <- dtWorker$full %>%
  group_by(
    Contact_dum,
    inNonDutch
  ) %>%
  summarise(
    n = n(),
    AttitudeM = mean(thermometerDutch_1, na.rm = T),
    AttitudeSD = sd(thermometerDutch_1, na.rm = T),
    AttitudeSE = AttitudeSD / sqrt(n),
    AttitudeLwr = AttitudeM - 1.96 * AttitudeSE,
    AttitudeUpr = AttitudeM + 1.96 * AttitudeSE
  ) %>%
  ungroup() %>%
  mutate(InteractionType = paste(
    ifelse(Contact_dum == 1, "Out", "NoOut"),
    ifelse(inNonDutch == 1, "In", "NoIn"),
    sep = ", "
  ))
